---
title: "Logistic Regression"
author: "M. Halley-Frame"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
# Store location of dataset into a variable called url
url <- "http://archive.ics.uci.edu/ml/machine-learning-databases/heart-disease/processed.cleveland.data"

# Extract and store data using read.csv into a variable called data
data <- read.csv(url, header=FALSE)

# Preview the first six rows of the dataset
head(data)

# Rename columns according to the data dictionary at the url source
colnames(data) <- c("age", "sex", "cp", "trestbps", "chol",
  "fbs", "restecg", "thalach", "exang", "oldpeak", "slope", "ca", "thal", "hd")

# Here we review the structure of the data and assess what needs to be cleaned up to the correct data type
str(data)

# Remove 0 and 1 numerics and replace with M/F then convert to a factor
data[data == "?"] <- NA
data[data$sex == 0,]$sex <- "F"
data[data$sex == 1,]$sex <- "M"
data$sex <- as.factor(data$sex)

# Convert all required variables into their factor requirement
data$cp <- as.factor(data$cp)
data$fbs <- as.factor(data$fbs)
data$restecg <- as.factor(data$restecg)
data$exang <- as.factor(data$exang)
data$slope <- as.factor(data$slope)

# Convert columns with missing data or "?" that we replaced with NA to ints first then factors
data$ca <- as.integer(data$ca)
data$ca <- as.factor(data$ca)

data$thal <- as.integer(data$thal)
data$thal <- as.factor(data$thal)

# Here we perform a test on the hd variable for 0 and if true, return healthy, else unhealthy
data$hd <- ifelse(test=data$hd == 0, yes="Healthy", no="Unhealthy")
data$hd <- as.factor(data$hd)

# Confirm all changes have taken effect on the dataframe
str(data)





```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
