---
title: "Logistic Regression"
author: "M. Halley-Frame"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
# Store location of dataset into a variable called url
url <- "http://archive.ics.uci.edu/ml/machine-learning-databases/heart-disease/processed.cleveland.data"

# Extract and store data using read.csv into a variable called data
data <- read.csv(url, header=FALSE)

# Preview the first six rows of the dataset
head(data)

# Rename columns according to the data dictionary at the url source
colnames(data) <- c("age", "sex", "cp", "trestbps", "chol",
  "fbs", "restecg", "thalach", "exang", "oldpeak", "slope", "ca", "thal", "hd")

# Here we review the structure of the data and assess what needs to be cleaned up to the correct data type
str(data)

# Remove 0 and 1 numerics and replace with M/F then convert to a factor
data[data == "?"] <- NA
data[data$sex == 0,]$sex <- "F"
data[data$sex == 1,]$sex <- "M"
data$sex <- as.factor(data$sex)

# Convert all required variables into their factor requirement
data$cp <- as.factor(data$cp)
data$fbs <- as.factor(data$fbs)
data$restecg <- as.factor(data$restecg)
data$exang <- as.factor(data$exang)
data$slope <- as.factor(data$slope)

# Convert columns with missing data or "?" that we replaced with NA to ints first then factors
data$ca <- as.integer(data$ca)
data$ca <- as.factor(data$ca)

data$thal <- as.integer(data$thal)
data$thal <- as.factor(data$thal)

# Here we perform a test on the hd variable for 0 and if true, return healthy, else unhealthy
data$hd <- ifelse(test=data$hd == 0, yes="Healthy", no="Unhealthy")
data$hd <- as.factor(data$hd)

# Confirm all changes have taken effect on the dataframe
str(data)

# Quantify the number of rows with NA values 
nrow(data[is.na(data$ca) | is.na(data$thal),])

# hd and thal had "?" values so we need to retrive all rows with NA values using OR
data[is.na(data$ca) | is.na(data$thal),]


nrow(data) # Returns the number of rows in data frame pre-removal

# Removes the values that are NA
data <- data[!(is.na(data$ca) | is.na(data$thal)),]

nrow(data) # Returns the number of rows in data frame post-removal

# Check all boolean values to ensure each hd state is balanced in the dataset
xtabs(~ hd + sex, data=data)
xtabs(~ hd + cp, data=data)
xtabs(~ hd + fbs, data=data)

# Only 4 patients have a result at level 1 which could interupt our ability to find the best line
xtabs(~ hd + restecg, data=data)


```

## Including Plots

You can also embed plots, for example:

```{r}
# We then run a generalised linear model with a binomial distribution as this makes it predict using logistic reg.
logistic <- glm(hd ~sex, data=data, family="binomial")

# Here the model is summarised. Follow up lesson on Deviance Residuals
summary(logistic)

# We can then run the model across all variables
logistic <- glm(hd ~ ., data=data, family="binomial")
summary(logistic)

# Pseudo R2
ll.null <- logistic$null.deviance/-2
ll.proposed <- logistic$deviance/-2

(ll.null - ll.proposed) / ll.null


1 - pchisq(2*(ll.proposed - ll.null), df=(length(logistic$coefficients)-1))

predicted.data <- data.frame(
  probability.of.hd=logistic$fitted.values,
  hd=data$hd)

predicted.data <- predicted.data[
  order(predicted.data$probability.of.hd, decreasing = FALSE),]
predicted.data$rank <- 1:nrow(predicted.data)

library(ggplot2)

ggplot(data=predicted.data, aes(x = rank, y = probability.of.hd)) +
  geom_point(aes(color=hd), alpha=1, shape=4, stroke=2) +
  xlab("Index") +
  ylab("Predicted probability of getting heart disease")

ggsave("heart_disease_probabilities.pdf")



```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
