---
title: "Tidyverse examples"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
# Data wrangling using tidyverse (50-80% of the effort of a data science project)
library(tidyverse)
library(ggplot2)
library(devtools)

```

## Including Plots

You can also embed plots, for example:

```{r, echo=TRUE}

# Data visualisation
# Basic xy plot with vehicle class mapped as color
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = class))

# Basic xy plot with no mapping
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = cyl, y = hwy))

# Maps alpha for transparency of points
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, alpha = class))

# Maps class of vehicle to shape but be careful, only 6 shapes will plot omitting any other class
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, shape = class))

# Makes all points blue
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")



```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
